

\documentclass[12pt]{article}
\usepackage{graphicx}

\begin{document}
































\section{User Stories}\label{User Stories}

\begin{enumerate}
    \item Example 1: Provide a customer with the ability to signup into the application
   
   As a Customer, I’d like to signup to the application by filling out some details, so that I could do login into the app.

     \item Example 2: Provide a customer with the ability to login into the application
   
   As a Customer, I’d like to login to the application by filling out some credentials, so that I could use the application features. 
   
   \item Example 3: Provide a customer with the ability to select food from various restaurants.
   
   As a Customer, I’d like to select different food items and put them into my cart, so that I could order them later by visiting cart. 
   
    \item Example 4: Provide a customer with the ability to order food from personal online cart.
   
   As a Customer, I’d like to order food items which i have already added into my cart, so that I could proceed with the payment options further.
    \item Example 5: Provide a customer with the ability to authorize payment by filling out payment details  onto payments page.
   
   As a Customer, I’d like to do payment of my bill, so that restaurant could start processing my order. 
   
    \item Example 6: Provide a customer with the ability to book table for a particular restaurant.
   
   As a Customer, I’d like to book a table for dine in into my favourite restaurant, so that I could enjoy my dine-in food with my family and friends. 
   
    \item Example 7: Provide a restaurant owner with the ability to add restaurant details.
   
   As a business owner, I’d like to add varoius details about restaurant and menu, so that customer will know more about the restaurant and menu foods. 
\end{enumerate}

\bibliographystyle{abbrv}
\bibliography{main}

\end{document}